### 2014-11-18 LongDataResearchNotes/ARModel.Rmd
Fixing the merge.
Should finalize the model.

Working with the Long Data and heading to an AR model
========================================================

@@

>>>>

Working with the Long Data and heading to an AR model
=======================================================

@@

```
Lets stick with this model and call it an imperfect but informative way of adding intent to forecast models.
